---
title: "Sta 320 Final Project"
author: "Michael Gao"
date: "April 24, 2016"
output: html_document
---

# Getting the data

I scraped data for tv ratings of all regular NCAA basketball games from sportsmediawatch.com and then scraped all of the rankings of that week from espn.com. This was done for two seasons: 2013-2014 and 2014-2015.

## Scraping the Ratings
```{r, echo=FALSE}
# Load in libraries
library(rvest)
library(dplyr)
library(lubridate)
library(stringr)
library(ggplot2)
library(rdd)
```


Load in the dataset generated from get_tvrankings:
```{r}
load('AllSeasons.Rdata')
#Change the date to posix format
AllSeasons$Date <- as.POSIXct(AllSeasons$Date, origin = origin, tz = "GMT")

# Add in a column that represents the date for Monday of that week (when basketball rankings come out)

AllSeasons$weekof <- NA

AllSeasons$weekof <- AllSeasons$Date + days(2-ifelse(wday(AllSeasons$Date)==1, yes = 8, no = wday(AllSeasons$Date)))

```

load in dataset generated from SeasonRanks:
```{r}
load('SeasonRanks.Rdata')

# Add in the years posthoc to match AllSeasons dataset
SeasonRanks$weekof <- NA
SeasonRanks$weekof[1:378] <- as.POSIXct(ymd(paste('2013',SeasonRanks$date[1:378])), origin = origin, tz = "GMT")
SeasonRanks$weekof[379:1127] <- as.POSIXct(ymd(paste('2014', SeasonRanks$date[379:1127])), origin = origin, tz = "GMT")
SeasonRanks$weekof[1128:nrow(SeasonRanks)] <- as.POSIXct(ymd(paste('2015', SeasonRanks$date[1128:nrow(SeasonRanks)])), origin = origin, tz = "GMT")
```


The following steps are done to make sure the datasets match in their values.
```{r}
# Post processing for AllSeasons to match formatting of SeasonRanks
# Change st to state
AllSeasons$College1 <- str_replace_all(AllSeasons$College1, 'St\\.', 'State')
# Change coll. to college
AllSeasons$College1 <- str_replace_all(AllSeasons$College1, 'Coll\\.', 'College')
# Change Conn to Connecticut
AllSeasons$College1 <- str_replace_all(AllSeasons$College1, '^Conn$', 'Connecticut')
# Change okla. to Oklahoma
AllSeasons$College1 <- str_replace_all(AllSeasons$College1, 'Okla\\.', 'Oklahoma')
# Change FSU to Florida State 
AllSeasons$College1 <- str_replace_all(AllSeasons$College1, 'FSU', 'Florida State')
# Change all of the saint schools
# UNC
AllSeasons$College1 <- str_replace_all(AllSeasons$College1, 'UNC', 'North Carolina')
# NC Central
AllSeasons$College1 <- str_replace_all(AllSeasons$College1, 'NC Central', 'North Carolina Central')
# Miami
AllSeasons$College1 <- str_replace_all(AllSeasons$College1, 'Miami \\(FL\\)', 'Miami')
# Michigan
AllSeasons$College1 <- str_replace_all(AllSeasons$College1, 'Mich\\.', 'Michigan')

# Weird encoding issue
stjoseph <- AllSeasons$College1[170]
AllSeasons$College1[AllSeasons$College1 == stjoseph] <- "Saint Joseph's"
stmarys <- AllSeasons$College1[267]
AllSeasons$College1[AllSeasons$College1 == stmarys] <- "Saint Mary's"
stjohns <- AllSeasons$College1[310]
AllSeasons$College1[AllSeasons$College1 == stjohns] <- "Saint John's"


# Same for College2
AllSeasons$College2 <- str_replace_all(AllSeasons$College2, 'St\\.', 'State')
AllSeasons$College2 <- str_replace_all(AllSeasons$College2, 'Coll\\.', 'College')
AllSeasons$College2 <- str_replace_all(AllSeasons$College2, '^Conn$', 'Connecticut')
AllSeasons$College2 <- str_replace_all(AllSeasons$College2, 'Okla\\.', 'Oklahoma')
AllSeasons$College2 <- str_replace_all(AllSeasons$College2, 'FSU', 'Florida State')
AllSeasons$College2[AllSeasons$College2 == stjoseph] <- "Saint Joseph's"
AllSeasons$College2[AllSeasons$College2 == stmarys] <- "Saint Mary's"
AllSeasons$College2[AllSeasons$College2 == stjohns] <- "Saint John's"
AllSeasons$College2 <- str_replace_all(AllSeasons$College2, 'UNC', 'North Carolina')
AllSeasons$College2 <- str_replace_all(AllSeasons$College2, 'NC Central', 'North Carolina Central')
AllSeasons$College2 <- str_replace_all(AllSeasons$College2, 'Miami \\(FL\\)', 'Miami')
AllSeasons$College2 <- str_replace_all(AllSeasons$College2, 'Mich\\.', 'Michigan')

# Convert Viewers to a number value:
convert_to_number <- function(x){
  if (is.na(x)){
    return(NA)
  }
  else if (substr(x,nchar(x),nchar(x)) == 'M'){
    return(as.double(substr(x,1,nchar(x)-1)) * 1000000)
  }
  else if (substr(x,nchar(x),nchar(x)) == 'K'){
    return(as.double(substr(x,1,nchar(x)-1)) * 1000)
  }
  else {
    return(NA)
  }
}


AllSeasons$num_viewers <- sapply(AllSeasons$Vwrs., convert_to_number)

# In SeasonRanks
SeasonRanks$teams <- str_replace_all(SeasonRanks$teams, 'Wichita St', 'Wichita State')
SeasonRanks$teams <- str_replace_all(SeasonRanks$teams, "St John", "Saint John's")
```


Calculate the gameranking for each game
```{r}
# Remove missing values in AllSeasons
AllSeasons <- na.omit(AllSeasons)
# For each match in AllSeasons and SeasonRanks for the weekof column, fill in the corresponding rank if it exists

AllSeasons$college1rank <- NA

for(row in 1:nrow(AllSeasons)){
  tempweekof <- AllSeasons$weekof[row]
  tempdf <- SeasonRanks %>% filter(weekof == tempweekof)
  for(temp in 1:nrow(tempdf)){
    if(AllSeasons$College1[row] == tempdf$teams[temp]){
      AllSeasons$college1rank[row] <- SeasonRanks$ranks[temp]
    }
  }
}

AllSeasons$college2rank <- NA

for(row in 1:nrow(AllSeasons)){
  tempweekof <- AllSeasons$weekof[row]
  tempdf <- SeasonRanks %>% filter(weekof == tempweekof)
  for(temp in 1:nrow(tempdf)){
    if(AllSeasons$College2[row] == tempdf$teams[temp]){
      AllSeasons$college2rank[row] <- SeasonRanks$ranks[temp]
    }
  }
}
```


```{r}
# New column: gamerank

get_gamerank <- function(x){
  # x is a row number input
  if (all(is.na(c(AllSeasons$college1rank[x], AllSeasons$college2rank[x])))){
    return('Unranked')
  } else if (is.na(AllSeasons$college1rank[x]) & !is.na(AllSeasons$college2rank[x])){
    return(AllSeasons$college2rank[x])
  } else if (is.na(AllSeasons$college2rank[x]) & !is.na(AllSeasons$college1rank[x])){
    return(AllSeasons$college1rank[x])
  } else {
    return(min(c(AllSeasons$college1rank[x],AllSeasons$college2rank[x])))
  }
}

AllSeasons$gamerank <- sapply(1:nrow(AllSeasons), get_gamerank)
```


Normalize ranks and plot

```{r}

AllSeasons <- AllSeasons %>% filter(gamerank != "Unranked", !is.na(num_viewers))
AllSeasons$gamerank <- as.numeric(AllSeasons$gamerank)

# Normalize
AllSeasons$gamerank <- AllSeasons$gamerank - 25
# Create Treatment variable
AllSeasons$top25 <- (AllSeasons$gamerank <= 0) * 1

ggplot(data = AllSeasons, aes(x= gamerank, y = num_viewers)) + geom_point(aes(color = gamerank > 0), size = 4) + theme_bw() + labs(x = "Rank - 25", y = "Number of Viewers", title = "Number of Viewers vs. Rank")
```

Utilize RDD package which can be found at https://github.com/ddimmery/rdd or on CRAN. 

```{r}
rdest <- RDestimate(num_viewers ~ gamerank | Network, data = AllSeasons, cluster = AllSeasons$gamerank, cutpoint = 0.99, kernel = "triangular")
summary(rdest)
plot(rdest)
```


